Effects of rotation on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-02-27 paper/Analisis.tex
minor edits

Next, we  quantify the line by its full width at half maximum
(FWHM) and the peak positions. In the next subsection we take a look
at the escape fraction. We conclude the section by estimating the
expected line flux for top hat filters at a fixed center and varying
width.

@@

In Figure ~\ref{figure:maximumsvsvelocities} we present the position
of the maxima as a function of $V_{\rm max}$. For the photons emitted
in the line center we do not find any variation in the position of the
maxima in the range of explored parameter space. However in the
homogeneous case we can see how the maxima goes to $x_{m}=0$, meaning
that the double peak is converted into a single peak.

@@

@@

If we now study the effect of the optical depth $\tau$ in the maxima
position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the
optical depth increase the maximum position increase and this is a
well-known result (include references), we found that this result is
not modified by rotation.\\

Finally when we take into account the viewing angle Fig
~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on
it, but again there is a threshold for the homogeneous distribution in
which  the double peaked merged into a single peak but this time it is
just the angle of viewing effect.

% try a Nscatt plot as a function of theta
%explain the method
\subsection{Full Width at Half Maximum of the Lyman alpha line}
\label{sec:LW}

@@

@@

@@

>>>>

First we quantify the line by its full width at half maximum
(FWHM) and the peak positions. In order to interpret these results we
measure how the rotation affects the average number of scatterings
for each Lyman-alpha photon in the simulation. This help us to
introduce the next subsection on the escape fraction in our models
including dust. We conclude the section by estimating the
expected line flux for top hat filters at a fixed center and varying
width.

@@

In Figure ~\ref{fig:maximavsvelocity} we present the position
of the maxima as a function of $V_{\rm max}$. For the photons emitted
in the line center we do not find any variation in the position of the
maxima in the range of explored parameter space. However in the
homogeneous case we can see how the maxima goes to $x_{m}=0$, meaning
that the double peak is converted into a single peak.

@@

In Figure ~\ref{fig:maximavsangle} we present the position of the
maxima as a function of the viewing angle $\mu$ for all the optical
depths and rotational velocities and the two different photon
distributions [FALTA LA GRAFICA].

%Finally when we take into account the viewing angle Fig
%~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on
%it, but again there is a threshold for the homogeneous distribution in
%which  the double peaked merged into a single peak but this time it is
%just the angle of viewing effect.

@@

% try a Nscatt plot as a function of theta
%explain the method

@@

Finally we also report on the effect of the neutral Hydrogen
optical depth $\tau_{H}$ on the maxima position $x_{m}$
Figure~\ref{figure:maximavsOD}. We find that, at fixed
rotation velocity, the position of the maxima increases with optical
depth as expected from basic theoretical consideraions. We compare
our results with the expected theoretical escaling for an infinnite
slab.

\subsection{Average Number of Scatterings}

@@

We have seen in the previous section that rotation affects the number
of scatterings that

@@

\subsection{Integrated flux}
